### 2017-10-31 submission/supplemental.Rmd
add table S3

**Table S1: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Adenoma**

@@

**Table S2: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Carcinoma**

@@

**Table S3: **
\footnotesize
```{r supplemental_table3, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

**Table S1: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Stool Adenoma**

@@

**Table S2: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Stool Carcinoma**

@@

**Table S3: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Tissue Adenoma**

```{r supplemental_table3, echo=FALSE, message=FALSE, warning=FALSE}

temp_t3a <- read_csv("../data/process/tables/beta_perm_adn_unmatched_tissue_summary.csv")
temp_t3b <- read_csv("../data/process/tables/beta_perm_adn_matched_tissue_summary.csv")

table_s3 <- temp_t3a %>% 
  bind_rows(temp_t3b) %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = c("Lu", "Flemer", "Lu (Matched)"))

colnames(table_s3) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma n", "Control n")

kable(table_s3, format = "markdown", align = 'c', padding = 2)
```
